\textcolor{red}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-03-02 paper/eccv2020/sections/discussion.tex
pass over intro
Figure edits, first pass over discussion.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Limitations}
The performance of our method is highly dependent on the accuracy of the initial
depth map of the MDE algorithm.
%Since our method relies on the monocular depth estimate, the accuracy of the output depth map also relies on the performance of the initial depth estimate.
Our results demonstrate that when the MDE technique produces a depth map
with good ordinal accuracy, where the ordering of object depths is roughly correct, the
depth estimate can be corrected to produce accurate absolute depth. However, if
the ordering of the initial depths is not correct, these errors will not be corrected by our histogram matching procedure and may propagate to the final output depth map.

Additionally, since our method relies on a diffused pulsed laser, the laser
power is spread out over the entire scene. Accordingly, for distant scene points very
little light will return to the SPAD and it may be difficult to accurately
capture distant scene geometry in the histogram. Thus our method is best suited to short to medium-range scenes.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\paragraph{Limitations}

The performance of our method is highly dependent on the accuracy of the initial
depth map of the MDE algorithm.
%Since our method relies on the monocular depth estimate, the accuracy of the output depth map also relies on the performance of the initial depth estimate.
Our results demonstrate that when the MDE technique produces a depth map
with good ordinal accuracy, where the ordering of object depths is roughly correct, the
depth estimate can be corrected to produce accurate absolute depth. However, if
the ordering of the initial depths is not correct, these errors will not be
corrected by our histogram matching procedure and may propagate to the final
output depth map.

\edit{Furthermore, our system uses a SPAD and is therefore susceptible to pileup.
Because the SPAD must be quenched before it can
detect another photon, earlier photons
from closer objects may systematically prevent detection of photons from further
objects, causing strong distortion of the transient. Fortunately, at the expense of
longer acquisition times, pileup can be mitigated
to a large extent by operating in the low-flux regime
where the number of photon events per second is controlled to be at most 5\% the
number of laser pulses per second~\cite{Single photon paper}. Finally, even in
the high-flux regime, it is sometimes possible to
correct pileup computationally~\cite{felix pileup correction}.}

\edit{While our prototype shows results for scanned/summed measurements, our scanning prototype operates in the low-flux regime,
avoiding pileup. A hypothetical diffused SPAD prototype could also operate in
this low-flux regime, which would yield identical measurement models and identical
results. Figure~\ref{fig:hardware}(b)-(c) empirically shows that collecting and summing scanned
measurements is nearly identical to capturing diffused measurements. ?!We show
empirical comparisons between the two modes on a more complex scene in the supplement?!}

\edit{Even if diffused and scanned/summed measurements are equivalent
  computationally, they are not equivalent energetically. In the diffuse
  setting, }the laser
power is spread out over the entire scene. Accordingly, for distant scene points very
little light will return to the SPAD and it may be difficult to accurately
capture distant scene geometry in the histogram. Thus our method is best suited
to short to medium-range scenes. \edit{Nevertheless, assuming an indoor scene with
fluorescent bulbs and an ambient spectral irradiance of $I_A =
2~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
to the laser), we find that the laser power required to achieve a minimum SBR of 5 for a
diffuse scene at $r = 2$ m
and a field of view of $\theta = 40^\circ$ can be calculated as}
%
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 r^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
\end{equation} 
\edit{giving $P_{\text{min}}=21$ mW, less than the 60 mW of the Kinect. Note
  that this calculation involves only on the signal-to-background photon ratio,
  which is independent of the actual number of counts recorded per exposure. In
  other words, pileup and laser energy concerns may 
  be addressed entirely independently. As for acquisition time, at a 10 MHz
  pulse rate with
  a 5\% photon detection rate, it takes just two seconds to acquire a million
  photon events. This number is dependent on scene albedo, but all time-of-flight imaging
systems share this dependency.}
